---
title: "Notre dame safety department"
author: "Riddhi Sharma"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

Load in the Data
```{r}
labs <- read_excel("LISP_Data.xlsx", sheet="Lab Info Data")
```

```{r}
summary(labs$`LISP Assessment Score`)
```

```{r}
summary(labs$`Risk Assessment Score`)
```

```{r}
summary(labs$`Risk Matrix Tier`)
```

The values of Risk Assessment Score and Risk Matrix Tier look good, but I need to convert the LISP Assessment Score column to a float data type. I will filter out the VPPs and ensure all the remaining values fall within the range of 0 to 1.

```{r}
labs <- labs %>%
  filter(`LISP Assessment Score` != "VPP" & `LISP Assessment Score` != "N/A")

labs$`LISP Assessment Score` <- as.numeric(labs$`LISP Assessment Score`)
summary(labs$`LISP Assessment Score`)
```

Convert Risk Matrix Tier column as factor for segmenting scatter plot

```{r}
labs$`Risk Matrix Tier` <- as.factor(labs$`Risk Matrix Tier`)
```

Now, I will create a scatter plot of LISP Assessment Score against Risk Assessment Score and segment each point by Risk Matrix Tier.

```{r}
g_1 <- ggplot(labs,
              aes(y = `Risk Assessment Score`, 
                  x = `LISP Assessment Score`, 
                  color = `Risk Matrix Tier`)) + 
  geom_point() + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  scale_color_manual(values =  c("1" = "green", "2" = "blue", "3" = "red")) +
  labs(y = "Risk Assessment Score", 
       x = "LISP Assessment Score",
       color = "Risk Matrix Tier",
       title = "LISP Assessment Score v Risk Assessment Score and Risk Matrix Tier")

g_1

```

Loading the Data
First, I am downloading the BSL-2 Action items sheet from Excel


```{r}
library(readxl)
bsl_action <- read_excel("LISP_Data.xlsx", sheet="BSL-2 Action Items")
head(bsl_action)
```

Remove rows generate from Tableau and NAs

```{r}
library(dplyr)
library(tidyr)
bsl_action <- bsl_action[1:120,-c(22:31)]
```

#Visualizations


```{r}
library(ggplot2)
library(forcats)
g_1 <- ggplot(bsl_action,
              aes(x = fct_rev(fct_infreq(Department)))) + 
  geom_bar(fill="blue") + 
  coord_flip() +
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text = element_text(face="bold"),
        plot.title = element_text(hjust = 0.5)) +
  labs(y = "Number of Action Items", 
       x = "Department",
       title = "Number of Action Items per Department") +
  geom_text(stat='count', aes(label=..count..), hjust= -.5)

g_1
```


```{r}
g_2 <- ggplot(bsl_action,
              aes(x = fct_rev(fct_infreq(Category)))) + 
  geom_bar(fill="red") + 
  coord_flip() +
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text = element_text(face="bold"),
        plot.title = element_text(hjust = 0.5)) +
  labs(y = "Number of Action Items", 
       x = "Category",
       title = "Number of Action Items per Category") +
  geom_text(stat='count', aes(label=..count..), hjust= -.3)

g_2
```

What Question Numbers were most applicable for BSL-2 Action Items?

```{r}
bsl_action$Number <- as.factor(bsl_action$Number)

g_3 <- ggplot(bsl_action,
              aes(x = fct_rev(fct_infreq(Number)))) + 
  geom_bar(fill="steelblue4") + 
  coord_flip() +
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text = element_text(face="bold"),
        plot.title = element_text(hjust = 0.5)) +
  labs(y = "Number of Action Items", 
       x = "Question #",
       title = "Number of Action Items per Question No.") +
  geom_text(stat='count', aes(label=..count..), hjust= -.3)

g_3
```


Where are the locations of Repeat Findings? What Question Number?

```{r}
bsl_action %>%
  filter(`Repeat Findings` == "Yes") %>%
  distinct(Location, `Question #`, Question)

```

Heatmap of Action Statuses

```{r}
set.seed(32)
sample <- bsl_action[sample(length(bsl_action), 10),]

g_4 <- ggplot(sample, aes(y = Number, x = Location, fill = Status)) + 
    geom_tile() + 
    labs(x = "Location", y = "Question", fill = "Status") + 
  theme(axis.text.x = element_text(angle = 40, vjust = 0.5))
g_4 
```

